`flippant` -- An `R` package for the automated  analysis of dithionite

### 2015-09-16 inst/manuscript/manuscript.rmd
Settle on title and structure of 'Installation, Input Requirements and Main Features' section; First drafts of "Installation" and "Input Data" subsections;

#Main Features

>>>>

#Installation, Input Requirements and Main Features
##Installation
`flippant` has been integrated into the `bioconductor` collection of tools for 
biomedical data analysis [@huber_orchestrating_2015] and is thus installable and
loadable as follows from within a functioning `R` environment:
```{r eval = FALSE}
source("http://bioconductor.org/biocLite.R")
biocLite(pkgs = "flippant")
library(flippant)
```
The package depends on the following, automatically satisfied extensions to `R`
base functionality: `r flippant_dependencies`

##Input Data
To analyse raw data stemming from dithionite scramblase assays, `flippant` 
requires for each data point information as the path to the 
fluorometer-generated spectrum, the amount of protein used to reconstitute 
proteoliposomes, the volume used in the assay before and after addition of 
dithionite (to calculate a volume correction factor), the amount of lips 
present (to calculate a proteine to phospholipid ratio or PPR) etc. The 
following function generates a spreadsheet program-compatible tab-delimited 
`ASCII` template including column names, commentary, expected data type and the 
default used when ommited, supporting the user in providing the data needed in 
one table row per data point.
```{r echo = FALSE, comment = ""}
make.usage.section("scramblaseAssayInputTemplate", env = asNamespace("flippant"))
```
The application agnostic tab-delimited format must be maintained for the 
completed table, which is subjected to extensive input checks when read by 
`flippant`.

Spectral input data is read by `flippant` using the information provided in the
input template raw spectra produced by QuantaMaster fluorometer instruments 
(Photon Technology International,Inc., Edison, New Jersey) running software 
versions FelixGX v4.1 and Felix32 v1.20, respectively, as well as simple generic
tab-delimited spectrum representing file format with time (s) and fluorescence 
intensity containing columns are currently supported. File type determination is
handled algorythmically.

##Graphic Representation of Spectral Traces
```{r echo = FALSE, comment = ""}
make.usage.section("scramblaseAssayTraces", env = asNamespace("flippant"))
```

##Producing Protein To Phospholipid (PPR) Plots
```{r echo = FALSE, comment = ""}
make.usage.section("scramblaseAssayPlot", env = asNamespace("flippant"))
```

##Non-graphical Output of Analysis Results
```{r echo = FALSE, comment = ""}
make.usage.section("scramblaseAssayStats", env = asNamespace("flippant"))
```
